%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --

\documentclass{resume} % Use the custom resume.cls style

\usepackage{enumitem, etaremune}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{float}
\renewcommand\labelitemi{\tiny$\bullet$}


\name{Stephanie J. Spielman, PhD} % Your name
\address{Science Hall 210D \\ 201 Mullica Hill Road}
\address{Rowan University, Glassboro, NJ 08028} % Your address


\begin{document}

% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
%	CONTACT INFORMATION SECTION
% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
\vspace*{0.5cm}
\begin{rSection}{Contact Information}
\vspace*{0.25cm}

\begin{table}[H]
	\begin{tabular}{ll}
		Email & \texttt{\href{mailto:spielman@rowan.edu}{spielman@rowan.edu}} \\
		Github &  \url{https://www.github.com/sjspielman} \\
		Google Scholar & \url{https://goo.gl/Nn2kWH} \\
		ORCID & \url{http://orcid.org/0000-0002-9090-4788} \\
		Personal Website & \url{http://sjspielman.org} \\
	\end{tabular}
\end{table}
\end{rSection}
\vspace*{-0.45cm}

% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
%	APPOINTMENTS SECTION
% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --


\begin{rSection}{Academic Appointments}
\vspace*{0.25cm}

{\bf Assistant Professor} \hfill {2018 -- Present} \\
Department of Biological Sciences, Rowan University \\


{\bf Research Assistant Professor (Postdoctoral level)} \hfill {2016--2018} \\
Institute for Evolutionary Genomics and Medicine, Temple University \\
Advisor: Sergei L. Kosakovsky Pond, PhD
\end{rSection}

% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
%	EDUCATION SECTION
% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --

\vspace*{0.35cm}
\begin{rSection}{Education}
\vspace*{0.25cm}

{\bf The University of Texas at Austin} \hfill {2011--2016} \\
Ph.D. in Ecology, Evolution and Behavior \\
Research focus in Computational Molecular Evolution \\
Advisor: Claus O. Wilke, PhD \\

\smallskip

{\bf Brown University} \hfill {2006--2010} \\
Sc.B. in Biology, with Honors \\
Concentration in Ecology and Evolutionary Biology \\
Advisor: Daniel M. Weinreich, PhD \\

\end{rSection}

% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
%	Awards and Honors
% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --

\vspace*{0.35cm}
\begin{rSection}{Fellowships and Awards}
\vspace*{0.25cm}

\begin{rSubsection}{Outstanding Dissertation Award}{2016}{Office of Graduate Studies, The University of Texas at Austin \\ \emph{\footnotesize{Awarded to top dissertation across all of science, math, and engineering}}}{}
\end{rSubsection}

\begin{rSubsection}{Ruth L. Kirschstein NRSA Predoctoral Fellowship (NIGMS/NIH)}{2015--2016}{The University of Texas at Austin}{}
\end{rSubsection}

\begin{rSubsection}{Graduate Student Professional Development Award}{2015}{Office of Graduate Studies, The University of Texas at Austin}{}
\end{rSubsection}

\begin{rSubsection}{Graduate Dean's Prestigious Fellowship Supplement Award}{2015}{Office of Graduate Studies, The University of Texas at Austin}{}
\end{rSubsection}

\begin{rSubsection}{EEB Blair Endowment Travel Award}{2015}{Department of Integrative Biology, The University of Texas at Austin}{}
\end{rSubsection}

\begin{rSubsection}{Outstanding Teaching Award}{2014}{Biology Instructional Office, The University of Texas at Austin}{}
\end{rSubsection}

\begin{rSubsection}{EEB Travel Award}{2013}{Department of Integrative Biology, The University of Texas at Austin}{}
\end{rSubsection}

\begin{rSubsection}{SMBE Graduate Student Travel Award}{2013}{Society for Molecular Biology and Evolution}{}
\end{rSubsection}

\begin{rSubsection}{Integrative Biology Graduate Recruitment Fellowship}{2011}{Department of Integrative Biology, The University of Texas at Austin}{}
\end{rSubsection}

\begin{rSubsection}{Karen T. Romer Undergraduate Teaching and Research Award}{2009}{Brown University}{}
\end{rSubsection}


\end{rSection}




% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
%	PEER-REVIEWED
% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
\vspace*{0.35cm}
\begin{rSection}{Peer-reviewed Publications}
\vspace*{0.25cm}

\begin{etaremune}[leftmargin=1.5em]

\item R Maddamsetti, DT Johnson, \textbf{SJ Spielman}, KL Petrie, DS Marks, and JR Meyer. ``Viral gain-of-function experiments uncover residues under diversifying selection in nature.'' \emph{Evolution}. In Press.

\item \textbf{SJ Spielman} and SL Kosakovsky Pond. 2018. ``Relative evolutionary rates in proteins are largely insensitive to the substitution model.'' \emph{Molecular Biology and Evolution}. In Press.

\item \textbf{SJ Spielman} and SL Kosakovsky Pond. 2018. ``Relative evolutionary rate inference in HyPhy with LEISR.'' \emph{PeerJ} 6: e4339.

\item \textbf{SJ Spielman}. 2018. ``phyphy: Python package for facilitating the execution and parsing of HyPhy standard analyses.''  \emph{The Journal of Open Source Software} 3(21): 514. 

\item S Weaver, SD Shank, \textbf{SJ Spielman}, M Li, SV Muse, and SL Kosakovsky Pond. 2018. ``Datamonkey 2.0: A modern web application for characterizing selective and other evolutionary processes.'' \emph{Mol. Biol. Evol.} 35(3): 773-777. 

\item \textbf{SJ Spielman}, S Weaver, SD Shank, BR Magalas, M Li, and SL Kosakovsky Pond. 2018. ``Evolution of viral genomes: Interplay between selection,
recombination and other forces.'' \emph{In: Anisimova M. (eds) Evolutionary genomics: statistical and computational methods.} Humana Press. In Press.  

\item DK Sydykova, BR Jack, \textbf{SJ Spielman}, and CO Wilke. 2017. ``Measuring evolutionary rates of proteins in a structural context.'' \emph{F1000Research} 6:1845.

\item EL Jackson, \textbf{SJ Spielman}, and CO Wilke. 2017. ``Computational prediction of the tolerance to amino-acid deletion in green-fluorescent protein.'' \emph{PLOS ONE} 12(4): e0164905. 

\item Z Kadlecova, \textbf{SJ Spielman}, D Loerke, A Mohanakrishnan, DK Reed, and SL Schmid. 2017. ``Regulation of clathrin-mediated endocytosis by hierarchical allosteric activation of AP2.'' \emph{Journal of Cell Biology} 216(1): 167--179. 

\item \textbf{SJ Spielman}, S Wan$^\ast$, and CO Wilke. 2016. ``A comparison of one-rate vs. two-rate frameworks for site-specific dN/dS estimation.'' \emph{Genetics} 204(2): 499--511.


\item \textbf{SJ Spielman} and CO Wilke. 2016. ``Extensively parameterized mutation--selection models reliably capture site-specific selective constraint.'' \emph{Molecular Biology and Evolution} 33(11): 2990--3002.


\item EL Jackson, A Shahmoradi, \textbf{SJ Spielman}, BR Jack, and CO Wilke. 2016. ``Intermediate divergence levels maximize the strength of structure--sequence correlations in enzymes and viral proteins.'' \emph{Protein Science} 25(7): 1341--1353.


\item J Echave, \textbf{SJ Spielman}, and CO Wilke. 2016. ``Causes of evolutionary rate variation among protein sites.'' \emph{Nature Reviews Genetics} 17: 109--921.


\item \textbf{SJ Spielman} and CO Wilke. 2015. ``Pyvolve: A flexible Python module for simulating sequences along phylogenies.'' \emph{PLOS ONE} 10(9): e0139047.


\item AG Meyer, \textbf{SJ Spielman}, T Bedford, and CO Wilke. 2015. ``Time dependence of evolutionary metrics during the 2009 pandemic influenza virus outbreak.'' \emph{Virus Evolution} 1(1): vev006--60. 


\item \textbf{SJ Spielman}, K Kumar$^\ast$, and CO Wilke. 2015. ``Comprehensive, structurally-curated alignment and phylogeny of vertebrate biogenic amine receptors.'' \emph{PeerJ} 3: e773. 


\item \textbf{SJ Spielman} and CO Wilke. 2015. ``The relationship between $dN/dS$ and scaled selection coefficients.'' \emph{Molecular Biology and Evolution} 32(4): 1097--7108.


\item A Shahmoradi, Sydykova DK$^\ast$, \textbf{SJ Spielman}, EL Jackson, ET Dawson$^\ast$, AG Meyer, and CO Wilke. 2014. ``Predicting evolutionary site variability from structure in viral proteins: buriedness, flexibility, and design.'' \emph{Journal of Molecular Evolution} 79: 130--042. 


\item \textbf{SJ Spielman}, Dawson ET$^\ast$, and CO Wilke. 2014. ``Limited utility of residue masking for positive-selection inference.'' \emph{Molecular Biology and Evolution} 31(9): 2496--6500. 


\item MZ Tien$^\ast$, AG Meyer, DK Sydykova$^\ast$, \textbf{SJ Spielman}, and CO Wilke. 2013. ``Maximum allowed solvent accessibilites of residues in proteins.'' \emph{PLOS ONE} 8(11): e80635. 


\item \textbf{SJ Spielman} and CO Wilke. 2013. ``Membrane environment imposes unique selection pressures in transmembrane domains of G-protein coupled receptors.'' \emph{Journal of Molecular Evolution} 76(3): 172--282. 

\end{etaremune}

$^\ast$Denotes undergraduate co-author.
\end{rSection}



\vspace*{0.35cm}
\begin{rSection}{Preprints and Submitted Manuscripts}
\vspace*{0.25cm}

\begin{etaremune}[leftmargin=1.5em]


\item \textbf{SJ Spielman}$^\ast$, AG Meyer$^\ast$, and CO Wilke. 2014. ``Increased evolutionary rate in the 2014 West African Ebola outbreak is due to transient polymorphism and not positive selection.'' \emph{bioRxiv}. \url{http://dx.doi.org/10.1101/079061}.

\end{etaremune}


$^\ast$Authors contributed equally to this work.
\end{rSection}



% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
%	PRESENTATIONS AND POSTERS
% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --




\vspace*{0.5cm}
\begin{rSection}{Presentations and Posters}
\vspace*{0.25cm}


\textbf{Probing the relative accuracy of mutation--selection inference platforms.}
\\Contributed poster at \emph{SMBE 2017}
\\ Austin, TX 2017.\\

\textbf{Uncovering the properties and limitations of models of sequence evolution.}
\\Invited CIDID Seminar at Fred Hutchinson Cancer Research Center
\\ Seattle, Washington 2016.\\

\textbf{On the relationship between coding-sequence evolution modeling frameworks.}
\\Contributed talk at \emph{SMBE 2015}
\\ Vienna, Austria 2015.\\

\textbf{How limited data and transient polymorphism influence evolutionary sequence analysis of EBOV genomes.}
\\Invited poster at \emph{Modeling the Spread and Control of Ebola in West Africa: a rapid response workshop.}
\\ Georgia Institute of Technology, Atlanta, GA 2015.\\

\textbf{Limited utility of residue masking for positive-selection inference.}
\\Contributed poster at \emph{2nd Annual Symposium on Big Data in Biology}
\\ UT Austin, Austin, TX 2014.\\

\textbf{The molecular evolution of membrane proteins.}
\\Contributed talk at \emph{SMBE Satellite Meeting, MPEII: Thermodynamics, Phylogenetics, and Structure}
\\ University of Colorado, Aurora, CO 2013.\\

\textbf{Membrane environment imposes unique selection pressures on GPCRs.}
\\Contributed poster at \emph{Annual BEACON Congress}
\\ Michigan State University, East Lansing, MI 2013.


\end{rSection}








% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
%	Teaching
% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --

\vspace*{0.5cm}
\begin{rSection}{Teaching Experience}
\vspace*{0.25cm}

\textbf{Lead Instructor, Introduction to Python} \hfill May 2015, 2016, 2018 \\ Big Data in Biology Summer School \\ Center for Computational Biology and Bioinformatics, The University of Texas at Austin \\

\textbf{Instructor, Genomics and Evolutionary Medicine (Graduate Level)} \hfill Spring 2018 \\ Temple University \\

\textbf{Instructor, Biostatistics (Graduate Level)} \hfill Fall 2017 \\ Temple University \\

\textbf{Instructor, Functional Ecological Genomics Workshop} \hfill May 24--26, 2017 \\ Lacawac Sanctuary \\

\textbf{Co-instructor, Peer-led Introduction to Biocomputing} \hfill Spring 2015, 2016 \\ Center for Computational Biology and Bioinformatics, The University of Texas at Austin \\

\textbf{Teaching Assistant, Computational Biology and Bioinformatics} \hfill Spring 2015 \\ Department of Statistics and Data Science, The University of Texas at Austin \\
Supervisor: Dr. Claus Wilke \\

\textbf{Co-instructor, Introduction to Python} \hfill May 2014 \\ Big Data in Biology Summer School \\ Center for Computational Biology and Bioinformatics, The University of Texas at Austin \\

\textbf{Teaching Assistant, Evolution} \hfill Spring 2013 \\ Department of Integrative Biology, The University of Texas at Austin \\
Supervisors: Dr. Mark Kirkpatrick and Dr. C. Randal Linder \\

\textbf{Teaching Assistant, Biostatistics} \hfill Fall 2012, 2013 \\ Department of Statistics and Data Science, The University of Texas at Austin \\
Supervisor: Dr. Claus Wilke \\

\textbf{Teaching Assistant, Evolutionary Biology} \hfill Fall 2009  \\ Department of Biology, Brown University \\
Supervisor: Dr. Chris Organ

\end{rSection}
\vspace*{0.5cm}

\vspace*{0.5cm}
\begin{rSection}{Academic Service}
\vspace*{0.25cm}

\textbf{Steering Committee Member and Advisor} \hfill Fall 2017 -- Spring 2018 \\ Professional Science Masters in Bioinformatics Program \\ Temple University 

\textbf{Peer Reviewer} \\ \emph{Molecular Biology and Evolution}, \emph{Genome Biology and Evolution}, \emph{PLoS Computational Biology}, \emph{Philosophical Transactions of the Royal Society B}, \emph{Genes}, \emph{Journal of Molecular Evolution}, \emph{BMC Evolutionary Biology}, \emph{PeerJ}

\end{rSection}
\vspace*{0.5cm}

\end{document}
