\documentclass[line, margin]{res}
\usepackage{hyperref}
\setlength{\parindent}{0pt}

\begin{document}
\name{Stephanie J. Spielman}


\begin{resume}
\vspace{0.5cm}
\section{Contact Information}
	\href{mailto:stephanie.spielman@gmail.com}{stephanie.spielman@gmail.com} \\
	\url{https://sjspielman.github.io}
	
\vspace{0.75cm}
	
\section{Education}

\textbf{University of Texas at Austin}, Austin, TX. \hfill Expected May 2016 \\ Ph.D. in Ecology, Evolution, and Behavior. \\ Advisor: Claus O. Wilke.


\textbf{Brown University}, Providence, RI.  \hfill 2010 \\ Sc.B. in Biology, with Honors. \\ Advisor: Daniel M. Weinreich.

\vspace{0.75cm}

\section{Awards and Honors}

\textbf{Outstanding Teaching Award} \hfill 2014 \\ UT Austin, Biology Instructional Office.

\textbf{UT Austin EEB Travel Grant} \hfill 2013 \\ UT Austin, Department of Integrative Biology.

\textbf{UT Austin Integrative Biology Graduate Recruitment Fellowship} \hfill 2011 \\ UT Austin, Department of Integrative Biology.

\textbf{Undergraduate Teaching and Research Award} \hfill 2009 \\ Brown University.

\vspace{0.75cm}
		
		
\section{In Prep Manuscripts}

\emph{Large, structurally-curated alignment and phylogeny of vertebrate biogenic amine receptors.} \textbf{Spielman SJ}, Kumar K, Sedaghat A, and Wilke CO.

\vspace{0.75cm}

\section{Submitted Manuscripts}

\emph{The relationship between $dN/dS$ and scaled selection coefficients.} \textbf{Spielman SJ} and Wilke CO. In review, Mol Biol Evol.


\vspace{0.75cm}

\section{Peer-reviewed Publications}

\emph{Limited utility of residue masking for positive-selection inference.} \textbf{Spielman SJ}, Dawson ET, and Wilke CO. 2014. Mol Biol Evol 31(9):2496 - 2500.

\emph{Predicting evolutionary site variability from structure in viral proteins: buriedness, flexibility, and design.} Shahmoradi A, Sydykova DK, \textbf{Spielman SJ}, Jackson EL, Dawson ET, Meyer AG, and Wilke CO. 2014. J Mol Evol 79:130 - 142.

\emph{Maximum allowed solvent accessibilites of residues in proteins.} Tien MZ, Meyer AG, Sydykova DK, \textbf{Spielman SJ}, and Wilke CO. 2013. PLoS One 8(11):e80635.

\emph{Membrane environment imposes unique selection pressures in transmembrane domains of G-protein coupled receptors.} \textbf{Spielman SJ} and Wilke CO. 2013. J Mol Evol 76(3):172 - 182.

\vspace{0.75cm}


\section{Presentations \\ and Posters}

\textbf{Molecular Evolution of Membrane Proteins.} \hfill 2013 \\ Contributed talk at \emph{Mechanisms of Protein Evolution II} Conference, Aurora, CO.

\textbf{Membrane environment imposes unique selection pressures} \hfill 2013 \\ \textbf{on GPCRs.} \\ Contributed poster at \emph{Annual BEACON Congress}, East Lansing, MI.

\vspace{0.75cm}


\section{Teaching} 

\textbf{TA, Undergraduate Biostatistic} \hfill Fall 2013 \\ UT Austin, Department of Statistics and Data Science.

\textbf{TA, Undergradute Evolution.} \hfill Spring 2013 \\ UT Austin, Department of Integrative Biology.

\textbf{TA, Undergraduate Biostatistics.} \hfill Fall 2012 \\ UT Austin, Department of 
Statistics and Data Science. 

\textbf{TA, Undergraduate Evolutionary Biology.} \hfill Fall 2009 \\ Brown University, Department of Biology. 



\end{resume}
\end{document}